Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-14 prop_letter.tex
small things

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator~$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projectors $P_0$
  and $P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that the union
of classical sets $E_1\cup E_2$ is replaced by $P_0+P_1-P_0P_1$ in the
case of quantum projection operators~\cite{Griffiths2003}, the last
condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
is a direct counterpart of Eq.~(\ref{eq:classicalconvex}). Thus the
definition of QIVPM is an amalgamation of both classical IVPMs and
conventional quantum probability measures.

In Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
conventional quantum probability measures in the limit where the lower
and upper end of each interval coincide exactly. In the remainder of
this section, we will show that our definition of QIVPMs is consistent
with classical IVPMs in the sense that a restriction of QIVPMs to
commuting events recovers the definition of classical IVPMs.

\paragraph*{QIVPMs and Classical IVPMs.} To formalize this connection,
we first note that contrary to the case with conventional quantum
probability spaces, there is generally no unique state $\rho$
consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent
with a state $\rho$ and projector $P$ if the interval $\bar{\mu}(P)$
contains the exact probability calculated by the Born rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the Born
rule~\citep{Born1983,peres1995quantum,544199}.

>>>>

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator~$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projectors $P_0$
  and $P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that
the union of classical sets $E_1\cup E_2$ is replaced by
$P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of Eq.~(\ref{eq:classicalconvex}). Thus our
definition of QIVPMs merges classical IVPMs with conventional quantum
probability measures.

In Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
conventional quantum probability measures in the limit where each the
lower and upper end of each interval coincide exactly and the
intervals cover $[0,1]$. In this section, we will show that our
definition of QIVPMs is consistent with classical IVPMs in the sense
that a restriction of QIVPMs to commuting events recovers the
definition of classical IVPMs.

To formalize this connection between QIVPMs and classical IVPMs, we
first note that contrary to the case with conventional quantum
probability spaces, there is generally no unique state $\rho$
consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent
with a state $\rho$ and projector $P$ if the interval $\bar{\mu}(P)$
contains the exact probability calculated by the Born rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the Born
rule~\citep{Born1983,peres1995quantum,544199}.
